A fast unified model for parsing and sentence understanding

### 2016-03-15 writing/hard_stack_paper/batching_fig.tex
Slightly revised abstract, still work in progress.

    \begin{scope}[shift={(0.35in,-0.25in)}, frontier/.style={distance from root=60pt}]

@@

\caption{\label{fig:batching:good}A conventional sequence-based RNN, instantiated for two sentences.}
\end{subfigure}

@@

\caption{\label{fig:batching:bad}A conventional TreeRNN, instantiated for two sentences.}
\end{subfigure}

\caption{An illustration of two standard designs for sentence encoders. Note that the TreeRNN, unlike the sequence-based RNN, requires a substantially different connection structure for each sentence.}
\end{figure}

>>>>

    \begin{scope}[shift={(0.25in,-0.2in)}, frontier/.style={distance from root=60pt}]

@@

\caption{\label{fig:batching:good}A conventional sequence-based RNN for two sentences.}
\end{subfigure}

@@

\caption{\label{fig:batching:bad}A conventional TreeRNN for two sentences.}
\end{subfigure}

\caption{An illustration of two standard designs for sentence encoders. Note that the TreeRNN, unlike the sequence-based RNN, requires a substantially different connection structure for each sentence, making batched computation impractical.}
\end{figure}
